Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-01 paper-ieee-trans.tex
added changes

\documentclass[journal]{IEEEtran}
\usepackage{graphicx}
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

@@

@@

@@

@@

@@

@@

\begin{IEEEbiography}{D. Cristina Duma}
Biography text here.
\end{IEEEbiography}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{graphicx}
\usepackage{array}

\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

In the following we provide an overview of the main EC-projects that have dealt with the issue of software reliability. Table \ref{tab:eup} shows the various projects with their logo, short name, long name and duration.

\begin{table}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{List of EC-projects}
\label{tab:eup}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{p{1.6cm}p{1.5cm}p{3cm}l}
\hline
\hline
\\
Logo & Short Name & Long Name & Duration\\
\hline
\hline
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/datagrid}
\end{minipage}
    & DataGrid &
Research and Technological Development for an International Data GridTwo & 2001--2004\\
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/egee}
\end{minipage}
     & EGEE I, II, III &
Enabling Grids for E-sciencE & 2004--2010\\
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/etics}
\end{minipage}
     & ETICS 1, 2 &
E--Infrastructure for Testing, Integration and Configuration of Software & 2006-2010\\
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/emi}
\end{minipage}
     & EMI &
Europeean Middleware Initiative & 2010--2013\\
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/egi}
\end{minipage}
     & EGI-Inspire &
Integrated Sustainable Pan-European Infrastructure for Researchers in Europe
 & 2010--2014\\
\begin{minipage}{.3\textwidth}
\includegraphics[width=15mm,height=7.5mm]{images/indigo}
\end{minipage}
     & INDIGO-DataCloud &
INtegrating Distributed data Infrastructures for Global ExplOitation
 & 2015--2017\\
\hline
\hline
\end{tabular}
\end{table}

\subsection{DataGrid}

@@

\subsection{Enabling Grids for E--sciencE}

@@

\subsection{E--Infrastructure for Testing, Integration and Configuration of Software}

@@

\subsection{European Middleware Initiative}

@@

\subsection{EGI--Integrated Sustainable Pan--European Infrastructure}

@@

\subsection{INtegrating Distributed data Infrastructures for Global
ExplOitation}

@@

\begin{IEEEbiography}{Doina Cristina Duma}
Biography text here.
\end{IEEEbiography}
